Left-linear rewriting in adhesive categories

### 2024-04-24 concur/fusione.tex
typos

When dealing with left-linear rules, such a characterisation fails. Leaving aside the formal details (the interested reader can refer to \Cref{def:permcon}), the intuition is quite simple. In the linear case one proves that two derivations using the same rules in different orders are switch equivalent when the colimits of the two derivations, seen as diagrams, are isomorphic and the isomorphism properly commutes with the embeddings of the rules.

This result fails when considering left-linear
derivations. This is readily seen by considering derivations $\der{D}$
in Fig.~\ref{fi:derD} and $\der{D}'$ in Fig.~\ref{fi:derD1}. We
observed that $\der{D}$ and $\der{D}'$ are not switch equivalent.
% 
Still, it is easy to see that they are related by a consistent\todo{le definiamo solo nell'appendice}
permutation, which is the identity on productions. The colimit of
both derivations is a single node with a self-loop, i.e.~the
terminal object in $\cat{Graph}$, hence all commutativity requirements
are trivially satisfied.

@@

\begin{remark}
	\label{rem:church}
	It is worth to point out that, by
	\Cref{prop:switch,thm:switch_uni}, the derivation we obtain from
	\Cref{thm:church}\todo{missing} is made by two switchable derivations that will
	give back the starting derivation (up to abstraction equivalence),
	if switched again.

>>>>

When dealing with left-linear rules, such a characterisation
fails. Leaving aside the formal details (the interested reader can
refer to \Cref{def:permcon}), the intuition is quite simple. In the
linear case one proves that two derivations using the same rules in
different orders are switch equivalent when the colimits of the two
derivations, seen as diagrams, are isomorphic and the isomorphism
properly commutes with the embeddings of the rules. When considering
left-linear derivations, this is no longer true. Intuitively this is
due to the fact that the application of a rule can merge parts of an
object thus making the colimit little informative.
%
This effect can be seen for derivations $\der{D}$ in
Fig.~\ref{fi:derD} and $\der{D}'$ in Fig.~\ref{fi:derD1}. They are not
abstraction equivalent but the colimit of both derivations is a single node with a self-loop, i.e.~the terminal
object in $\cat{Graph}$, in a way that  all commutativity requirements are
trivially satisfied.
% OLD VERSION
% This is readily seen by considering derivations $\der{D}$
% in Fig.~\ref{fi:derD} and $\der{D}'$ in Fig.~\ref{fi:derD1}. We
% observed that $\der{D}$ and $\der{D}'$ are not switch equivalent.
% % 
% Still, it is easy to see that they are related by a consistent\todo{le definiamo solo nell'appendice}
% permutation, which is the identity on productions. The colimit of
% both derivations is a single node with a self-loop, i.e.~the
% terminal object in $\cat{Graph}$, hence all commutativity requirements
% are trivially satisfied.

@@

\begin{remark}
	\label{rem:church}
	It is worth to point out that, by
	\Cref{prop:switch,thm:switch_uni}, the derivation we obtain from
	\Cref{pr:church}\todo{missing} is made by two switchable derivations that will
	give back the starting derivation (up to abstraction equivalence),
	if switched again.
